---
title: "Watershed Delineation"
author: "Mark Hagemannr"
date: "3/31/2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r}
# update and load packages
# library(devtools)
# install_github('markwh/streamstats')
library(streamstats)
library(nhdplusTools)
library(sf)
library(dplyr)
```

Delineate watersheds to each sample point and USGS gage in NHC watershed. 
Calculate watershed area and percent ISC.

```{r}
setwd(metab_projdir)
sites <- read.csv("data/siteData/NHCsite_coordinates.csv", header=T, stringsAsFactors = F)
sites$ws_area.km2 <- NA
sites$isc.percent <- NA
```

```{r}
#pair with NHD flowlines
sites_sf <- sites[,1:4] %>% 
  st_as_sf(coords=c("longitude","latitude"),remove=F, crs=4326)

cur_nhd <- st_read(paste0(hypox_projdir, "/NHC_map/NHC_NHD_subset.gpkg")) 


# attach comids to each sample station
comid_points<- rep(NA, nrow(sites))
for(i in 1:nrow(sites_sf)){
  comid_points[i]<- discover_nhdplus_id(sites_sf[i,])  
}

sites$comid <- comid_points

nhd_dat <- cur_nhd[cur_nhd$comid %in% comid_points,] %>% 
  select(comid, slope)
sites <- left_join(sites, nhd_dat, by="comid")%>%
  select(-geom)



```

Function to delineate watershed and calculate area


(if timeout is reached before a result is returned, you can specify it using `setTimeout([number of seconds])`)

Here, `crs` is the coordinate reference system number (ESPSG spatial reference code). 

To see what it returned, the `leafletWatershed` function gives a simple interactive map.

```{r compute_ws_areas}
setTimeout(2000)
for(i in 1:nrow(sites)){
  dat <- sites[i,]
  WS <- delineateWatershed(xlocation = dat$longitude, ylocation = dat$latitude, crs = 4326, 
                           includeparameters = "true", includeflowtypes = "true" )
  WSchars <- computeChars(workspaceID = WS$workspaceID, rcode="NC")
  leafletWatershed(WS)
  params <- WSchars$parameters
  wsArea.miles2 <- params[params$code=="DRNAREA", 6]
  wsArea.km2 <- wsArea.miles2*(1.60934^2)  
  isc <- params[params$code=="LC11IMP",6]
  sites$ws_area.km2[i]<- wsArea.km2
  sites$isc.percent[i]<- isc
}



write.csv(sites, file = "/data/siteData/NHCsite_watersheds.csv", row.names=F)
```

